\documentclass[sigconf, anonymous]{acmart}

%\usepackage[colorlinks=true,citecolor=magenta,linkcolor=blue]{hyperref}
\usepackage{preamble}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{amsthm}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[]
\theoremstyle{definition}
\newtheorem{defn}{Definition}
%\theoremstyle{lemma}
%\newtheorem{lemma}{Lemma}
%\theoremstyle{corollary}
%\newtheorem{corollary}{Corollary}

\fancyhf{} % Remove fancy page headers
\fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2020} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
\acmConference[Anonymous Submission to ACM CCS 2020]{ACM Conference on Computer and Communications Security}{Due 15 May 2020}{London, TBD}
\acmYear{2020}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
% andri: at most 12 pages total

\begin{document}
\title{Non-Interactive Proofs of Proof-of-Work under Velvet Fork} % TODO: replace with your title

\begin{abstract}
Superlight clients allow decentralized wallets to learn facts about the blockchain without downloading all the block headers. They achieve exponentially faster communication compared to SPV clients. For proof-of-work, they implement the so-called NIPoPoW primitive, for which there exist two variants: Superblock clients and FlyClient. Both of these protocols require consensus changes to existing blockchains and at least a soft fork to implement. In this paper, we discuss how a blockchain can be upgraded to support superblock clients without a soft fork. We show that it is possible to implement the needed changes without modifying the consensus protocol and by requiring only a minority of miners to upgrade, an upgrade termed a ``velvet fork’' in the literature. While previous work conjectured that NIPoPoW can be safely deployed using velvet forks as-is, we show that previous constructions are insecure, and that using velvet techniques to interlink a blockchain can pose insidious security risks. We describe a novel attack which we term a ``chain-sewing’' attack which is only possible in velvet situations: An adversary can cut-and-paste portions of various chains from independent forks, sewing them together to form a proof that looks like a chain but is not. We demonstrate that a minority adversary can thwart previous constructions with overwhelming probability. We put forth the first provably secure velvet NIPoPoW construction. Our construction is secure against adversaries that are bounded by 1/4 of the upgraded honest miner population. We prove our construction achieves persistence and liveness and analyze the trade-offs between the upgraded population parameter and the succinctness of the construction. Like non-velvet NIPoPoWs, our approach allows proving generic predicates about chains using infix proofs and as such can be adopted in practice for fast synchronization of transactions and accounts.
\end{abstract}

% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10003029.10011703</concept_id>
<concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
% -- end of section to replace with generated code

\keywords{blockchain, consensus, lightclient, NIPoPoW}

\maketitle

\input{body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs}

\end{document}
